Evaluate fits

### 2023-02-03 Working Rmds/evaluate_fits.Rmd
Now organizing fits as S3 objects of class 'pkfit.' These are defined as a unique combination of dataset (DTXSID, Species, Study, Routes), data transformations (log-transform, dose-normalize, rescale time), fitting method (bobyqa or L-BFGS-B), and model (flat, 1-compartment, 2-compartment). They are structured as a list. Have written methods to create 'pkfit' object from fit and cvt tables, as well as methods for 'predict', 'residuals', and many other analysis tasks that are done at the single-fit level, like rmse, rsq, fractional residuals, etc.

# Import and preprocess CvTdb data

## Import CvTdb data

Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
```

@@

## Settings for pre-processing data

List of new_name = old_name to supply for preprocessing data

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized", #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Study_ID" = "studies.id",
  "Series_ID" = "series.id"
  )
```

List of default values for new columns added in preprocessing data

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "hours",
                      "Value.Units" = "mg/L")
```

## Preprocess data

```{r, eval = FALSE}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =names_list,
                       defaults_list =   defaults_list,
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       impute_loq = TRUE,
                       impute_sd = TRUE,
                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
                       suppress.messages = TRUE)

#save pre-processed data
# write.csv(cvt,
#           paste0("../inst/ext/cvt_preprocessed_",
#                  timestamp,
#           ".csv"),
#           row.names = FALSE)

cvt <- as.data.table(cvt)
rm(cvt_data)
```

```{r}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
                 "2023_01_23",
          ".csv"))
```

```{r}
cvt[, Conc_SD := Value_SD]
cvt[, Conc_SD_Dose := Value_SD_Dose]
```

@@

```{r}
fit_opts <- 
  as.data.table(
    expand.grid(
  rescale_time = c(FALSE, TRUE),
  fit_conc_dose = c(FALSE, TRUE),
  fit_log_conc = c(FALSE, TRUE))
  )

```

# Evaluate residuals for each set of fitting options

```{r, eval = FALSE}
eval_DT <- fit_opts[,
                  {
                    print(
                      paste("fit_log_conc = ",
                        fit_log_conc,
                        "; fit_conc_dose = ",
                        fit_conc_dose,
                        "; rescale_time = ",
                        rescale_time)
                    )

  #get fitting outputs file names
  fit_outputs <- dir(path = "../inst/ext",
      pattern = paste0("PK_fit_table_",
                       ".+",
        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "_fit_conc_dose_",
                        fit_conc_dose, "_",
                        "_rescale_time_",
                        rescale_time, "_"
                       ))

@@

  cat(paste0(paste(fit_outputs,
              collapse = "\n"), "\n"))

  #read in fitting outputs
  #flat model
  fit_flat <- fread(grep(x = fit_outputs,
                         pattern = "flat",
                         value = TRUE))
  #1compartment model
  fit_1comp <- fread(grep(x = fit_outputs,
                         pattern = "1compartment",
                         value = TRUE))
  #2compartment model
   fit_2comp <- fread(grep(x = fit_outputs,
                         pattern = "2compartment",
                         value = TRUE))

   fit_flat[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

    fit_1comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       fit_2comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

   cat("Evaluating residuals...\n")

   #evaluate residuals
   this_eval_DT <- evaluate_resids(cvt_pre = cvt,
                         fit_flat = fit_flat,
                         fit_1comp = fit_1comp,
                         fit_2comp = fit_2comp,
                         fit_conc_dose = fit_conc_dose,
                         fit_log_conc = fit_log_conc,
                         optimx_args = list(
                           "method" = "bobyqa",
                           "itnmax" = 1e6,
                           "control" = list("kkt" = FALSE)
                         ),
                         verbose = TRUE)

     write.csv(this_eval_DT,
                  paste("../inst/ext/evaluate_residuals_",
                        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "fit_conc_dose_",
                        fit_conc_dose, "_",
                        "rescale_time_",
                        rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

     this_eval_DT
                  },
  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]

write.csv(eval_DT,
          paste0("../inst/ext/eval_resid_",
          timestamp,
          ".csv"),
          row.names = FALSE)
```

Evalaute TK stats

```{r, eval = FALSE}
TKstats_DT <- fit_opts[,
                  {
                    print(
                      paste("fit_log_conc = ",
                        fit_log_conc,
                        "; fit_conc_dose = ",
                        fit_conc_dose,
                        "; rescale_time = ",
                        rescale_time)
                    )

  #get fitting outputs file names
  fit_outputs <- dir(path = "../inst/ext",
      pattern = paste0("PK_fit_table_",
                       ".+",
        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "_fit_conc_dose_",
                        fit_conc_dose, "_",
                        "_rescale_time_",
                        rescale_time, "_"
                       ))

  cat(paste0(paste(fit_outputs,
              collapse = "\n"), "\n"))

  #read in fitting outputs
  #flat model
  fit_flat <- fread(grep(x = fit_outputs,
                         pattern = "flat",
                         value = TRUE))
  #1compartment model
  fit_1comp <- fread(grep(x = fit_outputs,
                         pattern = "1compartment",
                         value = TRUE))
  #2compartment model
   fit_2comp <- fread(grep(x = fit_outputs,
                         pattern = "2compartment",
                         value = TRUE))

   fit_flat[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

    fit_1comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       fit_2comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       cat("Evaluating TK statistics...\n")
        #evaluate TK statistics & merge with postprocessed fits
   this_TKstats_DT <- evaluate_tkstats(cvt_pre = cvt,
                         fit_flat = fit_flat,
                         fit_1comp = fit_1comp,
                         fit_2comp = fit_2comp,
                         group_by = c("DTXSID",
                                          "Species",
                                          "Route",
                                          "Media"),
                         dose_norm = TRUE)

    write.csv(this_TKstats_DT,
                  paste("../inst/ext/evaluate_tkstats_",
                        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "fit_conc_dose_",
                        fit_conc_dose, "_",
                        "rescale_time_",
                        rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

     this_TKstats_DT
                  },
  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]

write.csv(TKstats_DT,
          paste0("../inst/ext/eval_TKstats_",
          timestamp,
          ".csv"),
          row.names = FALSE)

```

@@

```{r}
tk_DT <- fread(paste0("../inst/ext/eval_TKstats_",
          "2023_01_26",
          ".csv"))
```

```{r}
tk_DT[winmodel %in% "1compartment", AUC_oral_win := AUC_inf_oral_1mgkg.1compartment]
tk_DT[winmodel %in% "1compartment", AUC_iv_win := AUC_inf_IV_1mgkg.1compartment]
tk_DT[winmodel %in% "1compartment", tmax_win := tmax_oral.1compartment]
tk_DT[winmodel %in% "1compartment", Cmax_win := Cmax_oral_1mgkg.1compartment]

tk_DT[winmodel %in% "2compartment", AUC_oral_win := AUC_inf_oral_1mgkg.2compartment]
tk_DT[winmodel %in% "2compartment", AUC_iv_win := AUC_inf_iv_1mgkg.2compartment]
tk_DT[winmodel %in% "2compartment", tmax_win := tmax_oral.2compartment]
tk_DT[winmodel %in% "2compartment", Cmax_win := Cmax_oral_1mgkg.2compartment]
```

@@

```{r}
tk_DT_sub <- tk_DT[Analysis_Type %in% "Joint", .(fit_conc_dose, fit_log_conc, rescale_time, DTXSID, Species, Route, Media, AUC_inf_1mgkg, tmax, Cmax_1mgkg, AUC_oral_win, AUC_iv_win, tmax_win, Cmax_win, winmodel)]
```

@@

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_oral_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = FALSE")
```

@@

```{r}
ggplot(tk_DT_sub[rescale_time == TRUE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_oral_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = TRUE")
```

@@

@@

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_iv_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (IV)") +
  ylab("Winning model-predicted AUC_inf (IV)") +
  ggtitle("AUC_inf (IV), rescale_time = FALSE")
```

>>>>

# Import preprocessed CvTdb data

```{r}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
                 "2023_02_01",
          ".csv"))
```

@@

@@

```{r}
fit_opts <- 
  as.data.table(
    expand.grid(
  rescale_time = c(FALSE, TRUE),
  fit_conc_dose = c(FALSE, TRUE),
  fit_log_conc = c(FALSE, TRUE),
  log_trans = c(FALSE, TRUE),
  dose_norm = c(FALSE, TRUE),
  method = c("bobyqa", "L-BFGS-B"),
  model = c("flat", "1compartment", "2compartment"))
  )
```

# pkfit object

One "fitted model" is defined by the following information:

* Dataset used for fitting: A subset of `cvt` defined by the following information: 
    + DTXSID
    + Species
    + Studies.Analyzed
    + routes analyzed (that last one in the case when there was not enough oral absorption-phase data to fit kgutabs, but there was IV data, so we fit the IV data only)
* Analysis Type (error model): 
    + Joint: one set of params across all studies, but separate error SDs for each study
    + Separate: separate params & error SDs for each study
    + Pooled: one set of params & one error SD across all studies
* TK model:
    + flat
    + 1-compartment
    + 2-compartment
* Transformations applied to the data before fitting:
    + log transformation (fit_log_conc TRUE or FALSE)
    + dose-normalization (fit_conc_dose TRUE or FALSE)
    + rescaling time when study spanned days, weeks, months, or years (rescale_time TRUE or FALSE)
* Fitted model parameters
    + Name
    + Starting values
    + Lower & upper bounds
    + Fitted mean
    + Fitted standard deviation
* Information from `optimx`
    + Algorithm used
    + Control parameters used
    + Convergence code
    + Number of function evaluations
    + Message

We can make this into an R object, essentially just a list with all of this information. Call it an object of class `pkfit` that inherits from class `list`.

Then we can write methods to do things like predict, residuals, coeffs, get TK summary stats, etc. etc.

We can also write a "plot" method to plot concentration vs. time with the fitted curve.

## A pkanalysis object

One "analysis" is a set of three "fit" objects: one for each of the three models, for the same dataset, analysis type, and fitting options. We can call this an object of class `pkanalysis`. Duplicated information (e.g. dataset) will be stored only once.

Methods for a `pkanalysis` object include getting the winning model, and calculating the "p-value" for each model compared to the flat model (exp(AIC_model - AIC_flat)/2).

We can also get predictions, coeffs, resids, etc. but these will always return a list of 3 items, one for each model.

The "plot" method for a `pkanalysis` object plots concentration vs. time with all three fitted curves, or with only the winning fitted curve.

## Creating fitted objects from tables of fitted parameters & of pre-processed data

It would be unwieldy to save lots of R objects for each fit, especially since the fitted dataset would be the same for many fits. Instead, we have saved the fit output data as a table. To get the fitted dataset, we have to index into the appropriate pre-processed version of CvT, taking the appropriate subset of DTXSID, Species, studies analyzed, and routes analyzed.

We can write a method `pkfit()` to take one row of a fit output data table, and the full CvT pre-processed table, and produce a `pkfit` object.

# Evaluate residuals for each fit

```{r}
verbose <- FALSE
timestamp <- "2023_02_01"
resids_all <- fit_opts[,
         {
           #Read in fits
        #get fitting outputs file names
  fit_outputs <- dir(path = "../inst/ext",
      pattern = paste0("PK_fit_table_",
                       model,
        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "fit_conc_dose_",
                        fit_conc_dose, "_",
                        "rescale_time_",
                        rescale_time, "_",
        "method_", method,
        "_", timestamp
                       ))

  fit_outputs <- paste0("../inst/ext/",
                        fit_outputs)
  if(verbose %in% TRUE){
  cat(paste0(paste(fit_outputs,
              collapse = "\n"), "\n"))
  }

  #read in fitting output table for this model
  fit <- fread(grep(x = fit_outputs,
                         pattern = model,
                         value = TRUE))

  #now: go by DTXSID, Species, Analysis Type.
  fit[, {
    if(verbose %in% TRUE){
    cat(paste("DTXSID = ", DTXSID, "\n",
              "Species = ", Species, "\n",
              "Analysis Type = ", Analysis_Type, "\n",
              "Studies Analyzed = ", Studies.Analyzed, "\n"))
    }
    obj <- pkfit(fit = .SD,
                    dat = cvt)
    rmse <- rmse.pkfit(obj,
                       log_trans = log_trans,
                       dose_norm = dose_norm)
    rsq <- rsq.pkfit(obj,
                       log_trans = log_trans,
                       dose_norm = dose_norm)
    # error_sd <- overall_error_sd.pkfit(obj,
    #                    log_trans = log_trans,
    #                    dose_norm = dose_norm)

    #calculate residuals
    frac_resids <- frac_resids.pkfit(obj,
                           dose_norm = dose_norm,
                           log_trans = log_trans)
    #normalize residuals by 
    list("RMSE" = rmse,
         "rsq" = rsq,
         # "error_sd" = error_sd,
         "frac_resids.mean" = mean(frac_resids),
         "frac_resids.median" = median(frac_resids),
         "frac_resids.min" = min(frac_resids),
         "frac_resids.max" = max(frac_resids))
  },
  by = .(DTXSID, Species, Analysis_Type, Studies.Analyzed, LogLikelihood, AIC),
  .SDcols = names(fit)]
         },
  by = .(rescale_time,
         fit_conc_dose,
         fit_log_conc,
         log_trans,
         dose_norm,
         method,
         model)]
```

Evaluate TK stats.

This one will go a little bit differently. We'll loop over only the fitting options; then within that loop, we'll loop over a list of the possible models, and get the TK stats for each of those models. Then we'll rowbind the resulting list of three data.tables together. It needs to be done this way because the table of TK stats has different variable names depending on the model, so `data.table` can't row-bind them together directly inside the square brackets.

```{r}
fit_opts2 <- unique(fit_opts[, .(rescale_time,
         fit_conc_dose,
         fit_log_conc,
         method)])

model_list <- c("flat",
                "1compartment",
                "2compartment")

out_DT_list <- sapply(model_list,
                      function(this_model){
                        fit_opts2[,
                                  {
                                    #Read in fits
                                    #get fitting outputs file names
                                    fit_outputs <- dir(path = "../inst/ext",
                                                       pattern = paste0("PK_fit_table_",
                                                                        this_model,
                                                                        "_fit_log_conc_",
                                                                        fit_log_conc, "_",
                                                                        "fit_conc_dose_",
                                                                        fit_conc_dose, "_",
                                                                        "rescale_time_",
                                                                        rescale_time, "_",
                                                                        "method_", method,
                                                                        "_", timestamp
                                                       ))

@@

                                    if(verbose %in% TRUE){
                                      cat(paste0(paste(fit_outputs,
                                                       collapse = "\n"), "\n"))
                                    }

                                    #read in fitting output table for this model
                                    fit <- fread(grep(x = fit_outputs,
                                                      pattern = this_model,
                                                      value = TRUE))

                                    fit[, {
                                      if(verbose %in% TRUE){
                                        cat(paste("DTXSID = ", DTXSID, "\n",
                                                  "Species = ", Species, "\n",
                                                  "Analysis Type = ", Analysis_Type, "\n",
                                                  "Studies Analyzed = ", Studies.Analyzed, "\n"))
                                      }
                                      #create a 'pkfit' object
                                      obj <- pkfit(fit = .SD,
                                                      dat = cvt)
                                      #calculate the TK stats for this object
                                      tk <- calc_TK_stats.pkfit(obj)
                                      nca <- as.data.frame(
                                        nca.pkfit(obj,
                                                  dose_norm = TRUE)
                                      )
                                      cbind(tk, nca)
                                    },
                                    by = .(DTXSID,
                                           Species,
                                           Analysis_Type,
                                           Studies.Analyzed,
                                           LogLikelihood,
                                           AIC),
                                    .SDcols = names(fit)
                                    ]
                                  },
                                  by = .(fit_log_conc,
                                         fit_conc_dose,
                                         rescale_time,
                                         method),
                                  .SDcols = names(fit_opts2)
                        ]
                      },
                      simplify = FALSE,
                      USE.NAMES = TRUE)

 out_DT <- rbindlist(out_DT_list,
                     use.names = TRUE,
                     fill = TRUE,
                     idcol = "model")
```

@@

@@

```{r}
tk_DT_sub <- out_DT[Analysis_Type %in% "Joint", ]
```

Get the winning model and the p-value vs. flat model.

```{r}
setorder(tk_DT_sub,
         method,
         rescale_time,
         fit_conc_dose,
         fit_log_conc,
         DTXSID,
         Species,
         Studies.Analyzed,
         AIC)

tk_DT_sub[, winmodel := model[1],
          by = .(method,
         rescale_time,
         fit_conc_dose,
         fit_log_conc,
         DTXSID,
         Species,
         Studies.Analyzed)]

#p-value vs. flat model
tk_DT_sub[, AIC_flat := AIC[model %in% "flat"], by = .(method,
         rescale_time,
         fit_conc_dose,
         fit_log_conc,
         DTXSID,
         Species,
         Studies.Analyzed)]
tk_DT_sub[, rel_like_of_flat := exp((AIC - AIC_flat)/2)]
```

@@

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE &
                   model == winmodel &
                   method %in% "bobyqa"],
       aes(x = nca.oral.AUC_inf_1mgkg,
           y = AUC_inf_oral_1mgkg)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = FALSE")
```

@@

```{r}
ggplot(tk_DT_sub[rescale_time == TRUE &
                   model == winmodel &
                   method %in% "bobyqa"],
       aes(x = nca.oral.AUC_inf_1mgkg,
           y = AUC_inf_oral_1mgkg)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = TRUE")
```

@@

What are some examples when model-preidcted AUC is very big?

```{r}
tk_DT_sub[rescale_time == TRUE &
                   model == winmodel &
                   method %in% "bobyqa" &
            AUC_inf_oral_1mgkg > 1e5 &
            fit_log_conc %in% TRUE &
            fit_conc_dose %in% FALSE,
          .(DTXSID, Species, model, rel_like_of_flat)]
```

@@

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE &
                   model == winmodel &
                   method %in% "bobyqa"],
       aes(x = nca.iv.AUC_tlast_1mgkg,
           y = AUC_inf_iv_1mgkg)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose),
             cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (IV)") +
  ylab("Winning model-predicted AUC_inf (IV)") +
  ggtitle("AUC_inf (IV), rescale_time = FALSE")
```
